---
title: "Campbell Cleaning"
author: "Adapted for FEF by LKremer"
date: "10/15/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

Script for cleaning water level data from TruTrak capacitance rods. 
Designed for surface water level measurements.
Cleaning and QA/QC steps include 

1) removing bad data
2) adjusting data for shifts in logger position
3) converting stage to water depth
4) checking results against manual measurements.

Requires capacitance rod raw data and manual measurement spreadsheet

#Setup

```{r}
#setwd('..') # back out of 'src' folder to access other folders in project if opening script directly
```


```{r, include=FALSE}

pkgTest <- function(x)
{
  if (x %in% rownames(installed.packages()) == FALSE) {
    install.packages(x, dependencies= TRUE)
  }
  library(x, character.only = TRUE)
}

# Make a vector of the packages you need
neededPackages <- c('tidyverse', 'lubridate', 'xts', 'dygraphs', 'ggrepel',
                    'knitr', 'plotly', 'reshape') #tools for plot titles 

# For every package in the vector, apply your pkgTest function
for (package in neededPackages){pkgTest(package)}


source('./functions/campbellFunctions.R') #load helper functions
```

#Clean By Site

###Load data with opn_concat
## requires same date format across all spreadsheets. I've been adding
the column formatted_dataetime in excel with:
 1. for dd/mm/yyyy hh:mm:ss '=REPLACE(MID(B2,4,20),4,0,LEFT(B2,3))+0'
 2. for d/m/yy hh:mm '=TEXT(VALUE(B2),"dd/mm/yyyy hh:mm")'
 

```{r}
interfiles <- './formatted_data/campbeldataloggers'
# possible years 2020, 2021, 2022
year <- '2020'
# only outlet sites have campbells: dh1, est_louis1, fc1, lexen1
site<- 'dh1'

# this function found in cambellFunctions.R, adds a column for data year
campb_raw_2020 <- opn_concat(interfiles, year, site)


```

# Another option to open all years and concatonate
# The same thing can be done for all sites, for loops can be nested or consider lapply()
```{r}
years <- c('2020', '2021')
campb_raw_allyr <- data.frame()

for (year in years){
  campb_raw <- opn_concat(interfiles, year, site)
  campb_raw_allyr <- rbind(campb_raw_allyr,campb_raw)
}

campb_raw_allyr$monthday<-as.factor(format(
campb_raw_allyr$datetime, format="%m-%d"))

campb_raw_allyr$doy <- as.numeric(format(campb_raw_allyr$datetime, "%j"))

```


```{r}
#quick plot of all variables for a single year

camp_raw_resh <- campb_raw_2020 %>%
  select(datetime, sc_us_us.cm, temp_c, cdom_ppb_qse, turb_ntu) %>%
  melt(., id.vars = 'datetime')

allvar <- ggplot(camp_raw_resh, aes(x = datetime, y = value, color = variable))+
  geom_line()

ggplotly(allvar)

```

```{r}
#quick plot of conductivity for all years

ggplot(data = campb_raw_allyr,
       mapping = aes(x = doy, y = sc_us_us.cm,  color = year)) +
  geom_point() +
  geom_line() +
  facet_grid(facets = year ~ .) +
  scale_x_continuous(labels = function(x) format(as.Date(as.character(x), "%j"), "%d-%b")) +
  theme_bw()
```

# or

```{r}
ggplot(data = campb_raw_allyr,
       mapping = aes(x = doy, y = sc_us_us.cm,  color = year)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(labels = function(x) format(as.Date(as.character(x), "%j"), "%d-%b")) +
  theme_bw()

```
###Create complete timeseries that includes any missing datetimes

```{r}
#check if collection interval is consistent in dataset. Code as written only handles one interval but can be modified if interval was changed. 
camp_raw_sub <- campb_raw_2020 %>%
  select(datetime, sc_us_us.cm, temp_c, cdom_ppb_qse, turb_ntu)

checkTimeSteps()

ts_interval<- camp_raw_sub$datetime[2] - camp_raw_sub$datetime[1]

##round datetime to nearest whole interval
camp_raw_sub <- camp_raw_sub %>%
  mutate(datetime = round_date(datetime, as.period(ts_interval)))

#create full timeseries 
full_ts <- tibble(datetime=seq.POSIXt(camp_raw_sub$datetime[1], camp_raw_sub$datetime[length(camp_raw_sub$datetime)], by=ts_interval))
camp_raw_sub <- full_join(full_ts,camp_raw_sub)

#identify missing timesteps:
miss_ts <- filter(camp_raw_sub, is.na(sc_us_us.cm))%>%
  pull(datetime)
length(miss_ts)
```

### NEED TO CHECK INSTALLATION DATES, THOUGH CAMPBELLS CANT REALLY COLLECT DATA UNTILL HOOKED UP, LIKELY IN THE FIELD. 


###save
```{r}
stage_final <- stage_adj%>%
      dplyr::select(location, site, datetime, wtr_depth,level_flag)
loc_site<- paste(location,site, sep='_')

interfiles <- './data/3_cleaned_stage_caprod'
file_path <- paste(interfiles,location,site, sep='/')
#saveRDS(stage_final, file=paste0('data/cln/wtr_lvl_',loc_site,'.csv'))
write_csv(stage_final, file=paste0(file_path, '_clean.csv'))

```



