---
title: "MiniDOT DO import and format"
author: "Lauren Kremer"
date: "20 May 2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

Script for cleaning dissolved oxygen data from PME MiniDOT loggers
Cleaning and QA/QC steps include 

1) import .txt files and format to df
2) look for missing time steps and anomalies
3) format date and time from 

#Setup

```{r, include=FALSE}
source('./functions/co2_DO_functions.R') #load helper functions

# Make a vector of the packages you need
neededPackages <- c('tidyverse', 'lubridate', 'xts', 'dygraphs', 'ggrepel','knitr', 'plotly') #tools for plot titles 

# For every package in the vector, apply your pkgTest function
for (package in neededPackages){pkgTest(package)}


```

#Clean By Site

###Load data with opn_txt_concat

```{r}
interfiles <- 'formatted_data/minidots_DO'
# possible locations: 'dh', 'est_louis', 'fool', 'lexen'
year <- '2021'
location <- 'dh'
site<- 'dh1'

DO_raw <- opn_txt_concat(interfiles, year, location, site) %>%
  tibble::rowid_to_column("ID") %>% #add an ID column to identify problem points 
  mutate(sample_year = year) #add a year column, this might be useful to something like a 
  #facet wrap to compare years across plots
```


```{r}
#quick plot of DO
DOplot <- ggplot(DO_raw, aes(datetime,DO_mgL)) +
  geom_line()

ggplotly(DOplot)
```


```{r}
#The Q actually stands for Quality and provides a estimation of the quality of each oxygen measurement. This patented feature is unique to miniDOT.
# other instrumentation has a similar plot to check battery voltage. 
DyQuality()

# this instrument also collects temperature data. look at DyTemp from stageFunctions.R if a comparison to air data is desired.
```


```{r}
# can check points against a rolling average.  Here checking against previous 5 points using base R (sapply)
DO_raw <- DO_raw %>%
 mutate(DO_mgL_avg = c(NA, NA, NA, NA, sapply(5:nrow(.), function(i) mean(DO_mgL[(i-4):i]))))

# plots actual, rolling average and ID along with any flags.
DyRawDO()
```

###Create complete timeseries that includes any missing datetimes
```{r}
#check if collection interval is consistent in dataset. Code as written only handles one interval but can be modified if interval was changed. 
checkTimeSteps()

ts_interval<- DO_raw$datetime[2] - DO_raw$datetime[1]

##round datetime to nearest whole interval
DO_raw <- DO_raw%>%
  mutate(datetime = round_date(datetime, as.period(ts_interval)))

#create full timeseries 
full_ts <- tibble(datetime=seq.POSIXt(DO_raw$datetime[1], DO_raw$datetime[length(DO_raw$datetime)], by=ts_interval))
DO_raw <- full_join(full_ts,DO_raw)


#identify missing timesteps:
miss_ts <- filter(DO_raw, is.na(DO_mgL))%>%
  pull(datetime)
length(miss_ts)

miss_ts
```
## FOR DH2022: There is a missing point every day at 8:09am every day and some air data before CO2 was dropped into stream ~9:00AM

###Clean Raw DO

```{r}
bad_id <- c(0:20)
maxgap = 6

DOadj <- mutate(DO_raw, DO_mgL = na.approx(ifelse(ID %in% bad_id, NA, DO_mgL), maxgap=maxgap, na.rm=F))

DOplot <- ggplot(DOadj, aes(datetime,DO_mgL)) +
  geom_line()

ggplotly(DOplot)
```


###save
```{r}

#DO_final <- DO_final %>%
#     dplyr::select(date, time, BV_volts, temp_C, DO_mg, Q)
#DO_final <- DO_adj%>%
#      dplyr::select(datetime, time_sec, BV_volts, temp_C, DO_mgL,   Q)
DO_final <- DO_raw %>%
  dplyr::mutate(date = format(datetime, format = "%Y-%m-%d")) %>%
  dplyr::mutate(time = format(datetime, format = "%H:%M:%S")) #saving time and date this way allows for re-upload 
#and date recognition in R once cleaned. 

DO_final <- DO_final %>%
     dplyr::select(date, time, BV_volts, temp_C, DO_mg, Q)

loc_site <- paste(year, location, site, sep='_')

cleanfiles <- 'clean_data/minidots_DO'

file_path <- paste(cleanfiles, year, location, site, sep='/')
#saveRDS(stage_final, file=paste0('data/cln/wtr_lvl_',loc_site,'.csv'))
write_csv(DO_final, file=paste0(file_path, '_clean.csv'))

```



