---
title: "co2_clean"
author: "Lauren Kremer"
date: "11/21/2021"
output: html_document
---

Script for CO2 data from OM-CP-VOLT101A Voltage Data Logger

1) removing bad data
2) adjusting data for shifts 

Requires CO2 raw data


```{r setup, include=FALSE}

source('./functions/co2_DO_functions.R') #load helper functions
# package loading function
pkgTest <- function(x)
{
  if (x %in% rownames(installed.packages()) == FALSE) {
    install.packages(x, dependencies= TRUE)
  }
  library(x, character.only = TRUE)
}

# Make a vector of the packages you need
neededPackages <- c('tidyverse', 'lubridate', 'xts', 'dygraphs', 'ggrepel','knitr', 'plotly') #tools for plot titles 

# For every package in the vector, apply your pkgTest function
for (package in neededPackages){pkgTest(package)}
```


#### Additional functions
Functions that open and concatenate formatted data files

```{r functions, include=FALSE}

# A universal function to open all caprod data for a 'site' to a list of dataframes
opn_as_dflist_22 <- function(interfiles, year, watershed, site) {
   file_path <- paste(getwd(), interfiles, year, watershed, site, sep='/')
   path_list <- paste(file_path, list.files(file_path), sep= '/')
   data <- lapply(path_list, function(x) {
      dat <- read.table(x, skip = 6, header = TRUE, sep = ",", row.names = NULL, as.is = TRUE)
      # for each item in path list, grab the cap_rod number
      if(colnames(dat[3]) == 'Voltage..mV.') {
      dat$co2_ppm = ((dat$Voltage..mV.*10000)/160)
      dat$Voltage_V = dat$Voltage..mV./1000
      names(dat)[names(dat) == 'Voltage..mV.'] <- 'Voltage_mV'
    } else {
      dat$co2_ppm = dat$Voltage..V. *3333.33
      dat$Voltage_mV = dat$Voltage..V.*1000
      names(dat)[names(dat) == 'Voltage..V.'] <- 'Voltage_V'
}
      return(dat)
   })
   
}

# Each year of data has been formatted a bit differently. Rather than reformatting each spreadsheet, 
# a function specific to each year should concatenate the list made by 'opn_as_dflist' 
concat_2022 <- function(data) {
   combined.data <- do.call(rbind, data)
   combined.data <- combined.data %>%
     mutate(datetime = lubridate::mdy(Date) + hms(Time)) %>%
     mutate(date = lubridate::mdy(Date)) %>%
     arrange(datetime) %>%
     distinct() %>%
     #dplyr::rename(., wtr_ht_pt = wtrhgt__2, wtr_ht_avg = wtrhgt__3, water_temp = wtemp_a_1) %>%               
     rowid_to_column(var='ID')
   return(combined.data)
}
```
 
```{r, include = FALSE}
interfiles <- 'formatted_data/stream_co2'
# possible locations: 'dh', 'est_louis', 'fool', 'lexen'
year <- '2022'
watershed <- 'dh'
site<- 'dh1'

dflist <- opn_as_dflist_22(interfiles, year, location, site)

co2_raw <- concat_2021(opn_as_dflist(interfiles, year, location, site))
```
Convert voltage to CO2:

CO2ppm= (XF−XZ)*V/Vmax +XZ 

where V is the measured voltage, XF is the full scale value for CO2 output XZ is the zero value, Vmax is the full scale DAC output 

Measurement range of the Vaisala sensor 0 - 10 000 ppm CO2

Voltage recorders have different ranges, some with +-3V DC, others with +-160mV DC (0.32V range)

160mV multiplier = high voltage ppm (10,000) / voltage range (160mV) = 62.5 ppm/mV = 62500 ppm/V
=((mV/1000)/3)*10000

3V multiplier = high voltage ppm (10,000) / voltage range (3V) = 3333.33 ppm/V 

*******MORE ON THIS LATER, FOR NOW (15 JUNE 2022), USING A CONVERSION OF MV TO V IF NEEDED, AND CALCULATING THE MULTIPLIER BASED ON A 3V DATALOGGER. 160MV MULTIPLIER AS ABOVE GIVES PPMS ~5000.


```{r,include = FALSE}

## This will convert a mV column to voltage and mV or V to CO2ppm.   For now, the statement will not delete the mV column, rather generate a mV column if V are provided. 

if(colnames(co2_raw[4]) == 'Voltage..mV.') {
  co2_raw$co2_ppm = ((co2_raw$Voltage..mV.*10000)/160)
  co2_raw$Voltage_V = co2_raw$Voltage..mV./1000
  names(co2_raw)[names(co2_raw) == 'Voltage..mV.'] <- 'Voltage_mV'
} else {
  co2_raw$co2_ppm = co2_raw$Voltage..V. *3333.33
  co2_raw$Voltage_mV = co2_raw$Voltage..V.*1000
  names(co2_raw)[names(co2_raw) == 'Voltage..V.'] <- 'Voltage_V'
}
```


```{r,include = FALSE}
#quick plot of voltage
co2_check_plot <- ggplot(co2_raw, aes(datetime,co2_ppm))+
  geom_line()

ggplotly(co2_check_plot)
```


```{r}
co2_raw_summ <- co2_raw %>%
  group_by(Date) %>%
  summarize(dmean_co2_ppm = mean(co2_ppm)) %>%
  mutate(date = lubridate::mdy(Date)) %>%
  select(., dmean_co2_ppm, date)

ggplot(co2_raw_summ, aes(date, dmean_co2_ppm)) +
  geom_line() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylab('CO2 (ppm)') +
  scale_y_continuous(breaks = round(seq(0, 500, by = 100),1)) +
  xlab('Date')

co2_raw <- merge(co2_raw, co2_raw_summ)
```


####Create complete timeseries to identify any missing datetimes from the dataframe
```{r checktime}
#check if collection interval is consistent in dataset. Function as written only handles one interval but can be modified if interval was changed. 
cat(paste('Datetime intervals greater than 1 include:', sep = ''), checkTimeSteps(), sep = "\n")


ts_interval<- stage_raw$datetime[2] - stage_raw$datetime[1]

##round datetime to nearest whole interval
stage_raw <- stage_raw%>%
  mutate(datetime = round_date(datetime, as.period(ts_interval)))

#create full timeseries 
full_ts <- tibble(datetime=seq.POSIXt(stage_raw$datetime[1], stage_raw$datetime[length(stage_raw$datetime)], by=ts_interval))
stage_raw <- full_join(full_ts,stage_raw, by='datetime')

#identify missing timesteps:
miss_ts <- filter(stage_raw, is.na(wtr_ht_pt)) %>%
  pull(datetime)
```

```{r}
#Dygraph for raw data - option to flag deviations by slope change 
DyRawCO2<- function(df=co2_raw,threshold = 0.002, flag='TRUE',max=8){
  if (flag){
    CO2_df <- mutate(co2_raw, flag = ifelse(c(0,abs(diff(co2_ppm)))/co2_ppm > threshold, 11, 10))
    tsCO <- xts(dplyr::select(CO2_df, datetime, ID, flag, co2_ppm, dmean_co2_ppm), order.by = CO2_df$datetime)
    dygraph(tsCO) %>% 
      dyAxis('y',label='ppm',valueRange = c(0, max(co2_raw$co2_ppm)))%>%
      dyAxis('y2',label='ID',independentTicks=T)%>%
      dySeries('ID',axis='y2')%>%
      dyRangeSelector() %>%
      #dyHighlight(highlightCircleSize = 4, 
      #        highlightSeriesBackgroundAlpha = 0.2,
      #        hideOnMouseOut = TRUE)%>%
      #dyOptions(drawPoints = TRUE, pointSize = 2)%>%
      dyLegend(show = "always")
  }else{
    tsCO<- xts(dplyr::select(CO2_df, datetime, ID, flag, co2_ppm, dmean_co2_ppm), order.by=CO2_df$datetime)
    dygraph(tsStage) %>% 
      dyAxis('y',label='mm',valueRange = c(-100, 10000))%>%
      dyAxis('y2',label='ID',independentTicks=T)%>%
      dySeries('ID',axis='y2')%>%
      dyRangeSelector() %>%
      #dyHighlight(highlightCircleSize = 4, 
      #        highlightSeriesBackgroundAlpha = 0.2,
      #        hideOnMouseOut = TRUE)%>%
      #dyOptions(drawPoints = TRUE, pointSize = 2)%>%
      dyLegend(show = "always")
  }
}


DyRawCO2(df=co2_raw,threshold = 0.2, flag='TRUE')
```

```{r}

```

