---
title: "Cap Rod Cleaning - Lexen Creek "
author: "Adapted for FEF by LKremer"
date: `r Sys.Date()`
output: html_document
editor_options: 
  chunk_output_type: console
---

Script for cleaning water level data from TruTrak capacitance rods. 
Designed for surface water level measurements.
Cleaning and QA/QC steps include 

1) removing bad data
2) adjusting data for shifts in logger position
3) converting stage to water depth
4) checking results against manual measurements.

Requires capacitance rod raw data and manual measurement spreadsheet

##Setup

```{r, include=FALSE}

pkgTest <- function(x)
{
  if (x %in% rownames(installed.packages()) == FALSE) {
    install.packages(x, dependencies= TRUE)
  }
  library(x, character.only = TRUE)
}

# Make a vector of the packages you need
neededPackages <- c('tidyverse', 'lubridate', 'xts', 'dygraphs', 'ggrepel','knitr', 'plotly') #tools for plot titles 

# For every package in the vector, apply your pkgTest function
for (package in neededPackages){pkgTest(package)}

source('./functions/stageFunctions.R') #load helper functions

#if(!require(devtools)) install.packages("devtools")
#devtools::install_github("kassambara/gg1pubr")
#install.packages("ggpubr")
library(ggpubr)
```
No 2020 data for Lexen

#2021

All data terminated 9/29/21 
```{r functions21, include=FALSE}

# A universal function to open all caprod data for a 'site' to a list of dataframes
opn_as_dflist <- function(interfiles, year, watershed, site) {
   file_path <- paste(getwd(), interfiles, year, watershed, site, sep='/')
   path_list <- paste(file_path, list.files(file_path), sep= '/')
   data <- lapply(path_list, function(x) {
      dat <- read.table(x, skip = 0, header = TRUE, sep = ",", row.names = NULL, as.is = TRUE)
      # for each item in path list, grab the cap_rod number
      dat$rod_no <- unlist(strsplit(unlist(strsplit(path_list[1], "_"))[8], "[.]"))[1]
      return(dat)
   })
}

# Each year of data has been formatted a bit differently. Rather than reformatting each spreadsheet, 
# a function specific to each year should concatenate the list made by 'opn_as_dflist' 

concat_2021 <- function(data) {
   drops <- c("formatted_datetime", 'sample')
   combined.data <- do.call(rbind, data)
   combined.data <- combined.data %>%
     mutate(datetime = lubridate::mdy_hm(datetime)) %>%
     arrange(datetime) %>%
     dplyr::distinct() %>%
     dplyr::rename(., wtr_ht_pt = wtrhgt__2, wtr_ht_avg = wtrhgt__3, water_temp = wtemp_a_1) %>%      rowid_to_column(var='ID') %>%
     select(-one_of(drops))
   return(combined.data)
}
```

##2021 - Lexen1

```{r importlexen1_21, include=FALSE} 
#, eval=FALSE
interfiles <- 'formatted_data/stage_caprod'
year <- 2021
watershed<- 'lexen'
site <- 'lexen1'

stage_raw <- concat_2021(opn_as_dflist(interfiles, year, watershed, site)) %>%
  drop_na()

```

```{r plot1lexen1_21}
#, eval=FALSE
#quick plot of stage

ggplot(stage_raw, aes(datetime,wtr_ht_pt))+
  geom_line() +
  labs(title=site,
        x ="Date", y = "water height point")

```

####Create complete timeseries to identify any missing datetimes from the dataframe
```{r checktimelexen1_21}
#, eval=FALSE
#check if collection interval is consistent in dataset. Function as written only handles one interval but can be modified if interval was changed. 
#checkTimeSteps()

ts_interval<- stage_raw$datetime[2] - stage_raw$datetime[1]

##round datetime to nearest whole interval
stage_raw <- stage_raw%>%
  mutate(datetime = lubridate::round_date(datetime, as.period(ts_interval)))

#create full timeseries 
full_ts <- tibble(datetime=seq.POSIXt(stage_raw$datetime[1], stage_raw$datetime[length(stage_raw$datetime)], by=ts_interval))
stage_raw <- full_join(full_ts,stage_raw)

#identify missing timesteps:
miss_ts <- filter(stage_raw, is.na(wtr_ht_pt)) %>%
  pull(datetime)
length(miss_ts)
```

###Clean Raw Stage

1) Plot temperature for quick checks
 
```{r chktemplexen1_21}
#, eval=FALSE

#check temp data
DyTemp(airtemp = 'n') #check function if have logger_temp, default is 'y'

```

2) Plot raw data with flag if raw level changes by more than 2%.
```{r plantflagslexen1_21}
#, eval=FALSE

#Raw stage plot
DyRawStage(df=stage_raw,threshold = 0.2, flag='TRUE')
```

3) Manually identify points to be removed or corrected using the flagged plot
```{r badidlexen1_21}
#, eval=FALSE
#lexen1
bad_id_lexen1_2021 <-  c(1177:1183, 2003:2008,2891:2896, 4011:4017, 4917:4921, 7077:7079, 8063:8067, 15125:15128)

#lexen1
vert_correction_lexen1_2021<- data.frame(ID = c(7381:16309), offset=c(0.002))%>%
  mutate(cumOffset = cumsum(offset))
  #17 from 7/2/noon 7381 16309 to 9/2 noon
bad_id <- bad_id_lexen1_2021
vert_correction <- vert_correction_lexen1_2021
```

4) Vertical adjustments
```{r correctlexen1_21}
#, eval=FALSE

#function to make vertical correction and interpolate between missing values 
stage_adj<- AdjStage(df=stage_raw, maxgap=8)%>%
    mutate(watershed = watershed)%>%
    mutate(site = site)%>%
    filter(ID > 154) %>% # beginning of stream data
    filter(ID < 30000) %>% # end of stream data
    mutate(level_flag = ifelse(wtr_ht_avg< -50, 'Below Logger',
    ifelse(wtr_ht_avg> 1050, 'Over Logger', 'In Range')))

#stageAdj<- AdjStage(maxgap=30)

```

#### Plot adjusted stage
```{r plot2lexen3}
#, eval=FALSE
#plot adjusted stage
dyStageAdj(df=stage_adj)

```

Plot adjusted values only:
```{r plot3lexen3}
#, eval=FALSE
dyStageAdjonly<- function(df= stageAdj,max=1200){
      tsStageAdj<- xts(dplyr::select(df, datetime, adj_wtr_ht,ID), order.by=df$datetime)
      dygraph(tsStageAdj) %>% 
            dyAxis('y',label='mm',valueRange = c(0, 300))%>%
            dyAxis('y2',label='ID',independentTicks=T)%>%
            dySeries('ID',axis='y2')%>%
            dyRangeSelector() %>%
            #dyHighlight(highlightCircleSize = 4, 
            #        highlightSeriesBackgroundAlpha = 0.2,
            #       hideOnMouseOut = TRUE)%>%
            dyOptions(drawPoints = FALSE, pointSize = 2)%>%
            dyLegend(show = "always")
}

dyStageAdjonly(df=stage_adj)

# Simple df of adjusted values for stacked plot (see below)
simplelexen1_21 <- stage_adj %>%
  select(datetime, adj_wtr_ht, site) %>%
  drop_na()
```


####Check manual measurements
```{r importmanuallexen1_21}
#, eval=FALSE
# load manual measurements
interfiles <- 'formatted_data/manual_measurements'
file_path <- paste(getwd(),interfiles,paste(year, '/', site,'.csv', sep = ""), sep='/')

manMeas <- read.table(file_path, skip=0, header=TRUE, sep=",", row.names = NULL, as.is = TRUE)

manMeas<- read.csv(file_path)%>%
      #timezone set to MST, change if loggers used MDT/MST
      mutate(datetime = round_date(mdy_hm(datetime, tz='America/Phoenix'),'30 minutes'))%>% 
      mutate(water_depth = dep_to_bed-dep_to_water)
```


```{r depthoffsetlexen1_21}
#, eval=FALSE
#choose a static depth to bed value. Here we are using a mean of manual bed measurements from the top of the caprod post
stat_to_bed <- manMeas%>%
  summarize(mean_dep_to_bed = mean(dep_to_bed,na.rm=T))%>%
  pull(mean_dep_to_bed)

manMeas_fil <- manMeas %>%
      #filter(watershed == watershed)%>%
      #filter(site == site)%>%
      dplyr::rename(., wtr_depth_not_static = water_depth) %>%
      mutate(man_wtr_dep_static = 10*(stat_to_bed - dep_to_water))
### 10 to convert mm to cm

depth_offset <- manMeas_fil %>%
  #slice_min(datetime)%>%
  left_join(stage_adj %>%
              dplyr::select(datetime, adj_wtr_ht))%>%
  mutate(depth_offset = man_wtr_dep_static-adj_wtr_ht)%>%
  pull(depth_offset)
```


```{r wtrdepthlexen1_21}
#, eval=FALSE
#start with 0 value, change if plots below suggest need for manual adjustment change value. 
manual_offset <- 0
# lexen1 = 
# lexen2 = 0
stage_adj <- stage_adj%>%
  mutate(wtr_depth = adj_wtr_ht + depth_offset + manual_offset)

stage_adj <- stage_adj%>%
  mutate(wtr_depth = adj_wtr_ht + depth_offset[1] + manual_offset)
```

####Compare cleaned water level to manual measurements
```{r plot4lexen1_21}
#, eval=FALSE
#plot difference between measured water depth and manual depth measurement
stage_adj <- as.data.frame(stage_adj)
stageAdj.man<- dplyr::left_join(manMeas_fil,stage_adj, by = 'datetime') %>%
      mutate(diff = man_wtr_dep_static-wtr_depth)

ggplot(stageAdj.man, aes(datetime, diff))+
  geom_point(size=3)+
  theme_minimal()
```


```{r plot5lexen1_21}
#, eval=FALSE
#plot water level time series with manual measurements as points
stage_check_plot<- stage_adj%>%
  dplyr::left_join(.,manMeas_fil, by = 'datetime') %>%
  ggplot(aes(datetime,wtr_depth))+
    geom_line()+
    geom_point(aes(datetime, man_wtr_dep_static),size=3,col='red')

ggplotly(stage_check_plot)
```

###Export cleaned data
```{r savelexen1_21}
#, eval=FALSE
stage_final <- stage_adj %>%
      drop_na() %>%
      mutate(date = lubridate::date(datetime)) %>%
      mutate(time = format(datetime, format = "%H:%M")) %>%
      dplyr::select(watershed, site, date, time, wtr_depth, level_flag) 
    
loc_site<- paste(watershed,site, sep='_') 

interfiles <- 'clean_data/stage_caprod'
file_path <- paste(getwd(), interfiles,year,watershed,site, sep='/')
#saveRDS(stage_final, file=paste0('data/cln/wtr_lvl_',loc_site,'.csv'))
write_csv(stage_final, file=paste0(file_path, '/',site, '_clean.csv'))

```



#2022
##2022 - Lexen1

Data termination date: 
```{r functions22, include=FALSE}

concat_2022 <- function(data) {
  drops <- c('sample')
  combined.data <- do.call(rbind, data)
  combined.data <- combined.data %>%
    mutate(datetime = lubridate::mdy_hm(datetime)) %>%
    drop_na() %>%
    arrange(datetime) %>%
    dplyr::distinct() %>%
    dplyr::rename(., wtr_ht_pt = wtrhgt__2, wtr_ht_avg = wtrhgt__3, water_temp = wtemp_a_1) %>%      rowid_to_column(var='ID') %>%
  select(-one_of(drops))
   return(combined.data)
}

```

```{r importlexen1_22, include=FALSE}
interfiles <- 'formatted_data/stage_caprod'
year <- 2022
watershed<- 'lexen'
site <- 'lexen1'

stage_raw <- concat_2022(opn_as_dflist(interfiles, year, watershed, site))

stage_raw <- stage_raw%>%
  set_names(c('ID','datetime','water_temp', 'wtr_ht_pt', 'wtr_ht_avg', 'rod_no'))

```


```{r plot1lexen1_22}
#quick plot of stage
ggplot(stage_raw, aes(datetime,wtr_ht_pt))+
  geom_line()

```


####Create complete timeseries to identify any missing datetimes from the dataframe
```{r checktimelexen1_22}
#check if collection interval is consistent in dataset. Function as written only handles one interval but can be modified if interval was changed. 
#checkTimeSteps()

ts_interval<- stage_raw$datetime[2] - stage_raw$datetime[1]

##round datetime to nearest whole interval
stage_raw <- stage_raw%>%
  mutate(datetime = lubridate::round_date(datetime, as.period(ts_interval)))

#create full timeseries 
full_ts <- tibble(datetime=seq.POSIXt(stage_raw$datetime[1], stage_raw$datetime[length(stage_raw$datetime)], by=ts_interval))
stage_raw <- full_join(full_ts,stage_raw)

#identify missing timesteps:
miss_ts <- filter(stage_raw, is.na(wtr_ht_pt)) %>%
  pull(datetime)
length(miss_ts)
```

###Clean Raw Stage

1) Plot temperature for quick checks
 
```{r chktemplexen1_22}

#check temp data
DyTemp(airtemp = 'n') #check function if have logger_temp, default is 'y'
```

2) Plot raw data with flag if raw level changes by more than 2%.
```{r plantflagslexen1_22}

#Raw stage plot
DyRawStage(df=stage_raw,threshold = 0.5, flag='TRUE')
```

3) Manually identify points to be removed or corrected using the flagged plot
For complex data adjustments where caprod seems to get 'reset' with every data download, these can be adjusted in 3 steps:
perform all 'decrease'
review these and decide on 'increase' adjustments (values drifted downward)
remove all 'badid', points recorded when caprod was out of water

 a. Make a dataframe that includes all values that need negative correction

```{r negshiftlexen1_22}
vertdecrfunc <- function(x,y,z) {
  vertcorr1 <- data.frame(ID = c(x:z), offset = (stage_raw$wtr_ht_avg[stage_raw$ID==c(z)]-stage_raw$wtr_ht_avg[stage_raw$ID==c(y)])/length(x:z)) %>% #take avg water height at first ID and subtract it 
  mutate(cumOffset = cumsum(offset))
  return(vertcorr1)
}
# working in a line from left to right
# Where x is the ID at the left of the series that you want to adjust (leftmost)
# y is the ID with the greatest 'drifted' water level (middle)
# z is the ID with the water level that you want to meet (rightmost)
vertdecrease <- do.call(rbind, mapply("vertdecrfunc", x = c(6929, 9506, 12545, 15015), y = c(7919, 11073, 12969, 16156), z = c(7932, 11076, 12972, 16161), SIMPLIFY = FALSE))

#14802, 16151, 16159
```


```{r}
#make vertical correction and interpolate between missing values 
stage_adj<- AdjSectionStage(df1=stage_raw, df2=vertdecrease, maxgap=8)%>%
    mutate(level_flag = ifelse(wtr_ht_avg< -50, 'Below Logger',
    ifelse(wtr_ht_avg> 1050, 'Over Logger', 'In Range')))
```


```{r plotnegadjlexen1_22}

#plot adjusted stage
dyStageAdj(df=stage_adj)
```


```{r posshiftlexen1_22}
# The key difference btwn above and next function is the intended adjustment direction. 
vertincrfunc <- function(x,y,z) {
  vertcorr1 <- data.frame(ID = c(x:z), offset = (stage_raw$wtr_ht_avg[stage_raw$ID==c(x)] - stage_raw$wtr_ht_avg[stage_raw$ID==c(y)])/(length(x:z)))%>%
  mutate(cumOffset = cumsum(offset))
  return(vertcorr1)
}

vertincrease <- vertincrfunc(16188, 17280, 17281)
  #do.call(rbind, mapply("vertincrfunc", x = c(18930), y = c(16155), z = c(16168), SIMPLIFY = FALSE))

vert_correction <- rbind(vertdecrease, vertincrease)
```

```{r}
#make vertical correction and interpolate between missing values 
stage_adj<- AdjSectionStage(df1=stage_raw, df2=vert_correction, maxgap=8)%>%
    mutate(level_flag = ifelse(wtr_ht_avg< -50, 'Below Logger',
    ifelse(wtr_ht_avg> 1050, 'Over Logger', 'In Range')))
```

```{r plotposadjlexen1_22}

#plot adjusted stage
dyStageAdj(df=stage_adj)
```

```{r badidlexen1_22}
#lexen1
bad_id_lexen1_2022 <-  c(7920:7935, 9061:9064, 11073:11076, 12969:12972, 13960:13966, 16156:16162, 17167:17173, 18161:18166)

bad_id <- bad_id_lexen1_2022
```

4) Vertical adjustments
will need to add 50mm
```{r correctlexen1_22}

#make vertical correction and interpolate between missing values 
stage_adj<- AdjSectionStage(df1=stage_raw, df2 = vert_correction, maxgap=30)%>%
    mutate(watershed = watershed)%>%
    mutate(site = site)%>%
    filter(ID > 3) %>% # beginning of stream data
    filter(ID < 22222) %>% # end of stream data
    mutate(level_flag = ifelse(wtr_ht_avg< -50, 'Below Logger',
    ifelse(wtr_ht_avg> 1050, 'Over Logger', 'In Range')))

```

#### Plot adjusted stage
```{r plot2lexen1_22}

#plot adjusted stage
dyStageAdj(df=stage_adj)

```

Plot adjusted values only:
```{r plot3lexen1_22}

dyStageAdjonly<- function(df= stageAdj,max=1200){
      tsStageAdj<- xts(dplyr::select(df, datetime, adj_wtr_ht,ID), order.by=df$datetime)
      dygraph(tsStageAdj) %>% 
            dyAxis('y',label='mm',valueRange = c(-100, 300))%>%
            dyAxis('y2',label='ID',independentTicks=T)%>%
            dySeries('ID',axis='y2')%>%
            dyRangeSelector() %>%
            #dyHighlight(highlightCircleSize = 4, 
            #        highlightSeriesBackgroundAlpha = 0.2,
            #       hideOnMouseOut = TRUE)%>%
            dyOptions(drawPoints = FALSE, pointSize = 2)%>%
            dyLegend(show = "always")
}

dyStageAdjonly(df=stage_adj)

# Simple df of adjusted values for stacked plot (see below)
simplelexen1_22 <- stage_adj %>%
  select(datetime, adj_wtr_ht, site) %>%
  drop_na()
```


####Check manual measurements
```{r importmanuallexen1_22}

#load manual measurements
interfiles <- 'formatted_data/manual_measurements'
file_path <- paste(getwd(),interfiles, paste(year, '/', site,'.csv', sep = ""), sep='/')

#manMeas <- read.table(file_path, skip=0, header=TRUE, sep=",", row.names = NULL, as.is = TRUE)

manMeas<- read.csv(file_path)%>%
      #timezone set to MST, change if loggers used MDT/MST
      mutate(datetime = round_date(mdy_hm(datetime, tz='America/Phoenix'),'30 minutes'))%>%
      mutate(water_depth = dep_to_bed-dep_to_water)
```


```{r depthoffsetlexen1_22}
#choose a static depth to bed value. Here we are using a mean of manual bed measurements from the top of the caprod post
stat_to_bed <- manMeas%>%
  summarize(mean_dep_to_bed = mean(dep_to_bed,na.rm=T))%>%
  pull(mean_dep_to_bed)

manMeas_fil <- manMeas %>%
      #filter(watershed == watershed)%>%
      #filter(site == site)%>%
      dplyr::rename(., wtr_depth_not_static = water_depth) %>%
      mutate(man_wtr_dep_static = 10*(stat_to_bed - dep_to_water))
### 10 to convert mm to cm

depth_offset <- manMeas_fil %>%
  slice_max(datetime)%>%
  left_join(stage_adj %>%
              dplyr::select(datetime, adj_wtr_ht)) %>%
  mutate(depth_offset = man_wtr_dep_static-adj_wtr_ht) %>%
  pull(depth_offset)
```


```{r wtrdepthlexen1_22}
#start with 0 value, change if plots below suggest need for manual adjustment change value. 
manual_offset <- 50
# lexen1 =
# lexen2 = 0
stage_adj <- stage_adj%>%
  rowwise %>%
  mutate(wtr_depth = adj_wtr_ht + depth_offset + manual_offset)

stage_adj <- stage_adj%>%
  mutate(wtr_depth = adj_wtr_ht + depth_offset[1] + manual_offset)
```

####Compare cleaned water level to manual measurements
```{r plot4lexen1_22}
#plot difference between measured water depth and manual depth measurement
stage_adj <- as.data.frame(stage_adj)

stageAdj.man<- dplyr::left_join(manMeas_fil,stage_adj, by = 'datetime') %>%
      mutate(diff = man_wtr_dep_static-wtr_depth)

ggplot(stageAdj.man, aes(datetime, diff))+
  geom_point(size=3)+
  theme_minimal()
```


```{r plot5lexen1_22}
#plot water level time series with manual measurements as points
stage_check_plot<- stage_adj%>%
  dplyr::left_join(.,manMeas_fil, by = 'datetime') %>%
  ggplot(aes(datetime,wtr_depth))+
    geom_line()+
    geom_point(aes(datetime, man_wtr_dep_static),size=3,col='red')

ggplotly(stage_check_plot)

```

###Export cleaned data
```{r savelexen1_22}
#stage_final <- stage_adj %>%
stage_final <- stage_adj %>%
      drop_na() %>%
      mutate(date = lubridate::date(datetime)) %>%
      mutate(time = format(datetime, format = "%H:%M")) %>%
        #dplyr::select(watershed, site, date, time, wtr_depth, level_flag) 
      dplyr::select(watershed, site, date, time, adj_wtr_ht, level_flag) 
    
loc_site<- paste(watershed,site, sep='_') 

interfiles <- 'clean_data/stage_caprod'
file_path <- paste(getwd(), interfiles,year,watershed,site, sep='/')
#saveRDS(stage_final, file=paste0('data/cln/wtr_lvl_',loc_site,'.csv'))
write_csv(stage_final, file=paste0(file_path, '/',site, '_clean.csv'))

```


## Plot years separate lines
```{r}
lexen_1 <- rbind(simplelexen1_21,simplelexen1_22) 

lexen_1 <-lexen_1 %>%
mutate(year = as.factor(year(datetime)), # A hack. Set year to 2018. Allows me to use a date axis
    date_foo = as.Date(paste(2021, format(datetime, "%m-%d"), sep = "-"))) 


lexen1_plot <- lexen_1 %>%
  ggplot(aes(x=date_foo, y=adj_wtr_ht, col=year, group=year)) +
  geom_line() +
  ggtitle("seasonal plot") +
  theme_minimal(base_size = 8) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b-%d")

lexen1_plot
```

```{r}

```

