---
title: "QA/QC HOBO water level logger data"
author: "Lauren Kremer"
date: "05/31/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

Script for cleaning water level data from HOBO U20L-01 water level loggers. Designed for surface water level measurements.
QA/QC steps include:

1) removing bad data
2) converting stage to water depth
3) checking results against manual measurements.

Requires HOBO raw data and manual measurement spreadsheet


```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Setup
pkgTest <- function(x)
{
  if (x %in% rownames(installed.packages()) == FALSE) {
    install.packages(x, dependencies= TRUE)
  }
  library(x, character.only = TRUE)
}

# Make a vector of the packages you need
neededPackages <- c('tidyverse', 'lubridate', 'xts', 'dygraphs', 'ggrepel', 'knitr', 'plotly') #tools for plot titles 

# For every package in the vector, apply your pkgTest function
for (package in neededPackages){pkgTest(package)}

source('./functions/pressure_stageFunctions.R') #load helper functions
```

### 1. QA/QC By Site

a. Open a specific site with opn_concat_psite function.
This will open all .csvs within a specified year and transect/site. 
The resulting dataframe should iclude all columns in .csv (renamed
to be short and interpretable) and added
columns for instrument serial number and a transect position where 
a transect is a stream location with its corresponding wells
(e.g. lw1 represents data from the left riparian well)

Check that data matches column names

```{r, warning=FALSE, comment=FALSE,}
interfiles <- 'formatted_data/stage_pressure'
year <- '2020'
# possible locations: 'dh', 'est_louis', 'fool', 'lexen'
location<- 'fool'
site<- 'fc2'

pstage_raw <- opn_concat_psite(interfiles, year, location, site)

```


```{r, echo = FALSE}
#quick plot of pressure
ggplot(pstage_raw, aes(datetime,pressure_kPa, color=position))+
  geom_line()

```

  b. Convert pressure to water level using data from the instrument in the  'atmospheric' transect position. 
  Water level (h) is given by h=(P-Pr)/(rho * g) where P is the pressure measured by the sensor in the stream, Pr is the pressure measured by the reference sensor (atmospheric pressure), rho is the density of the water in the stream, and g is the acceleration due to gravity.

The density of water is temperature dependent, however, our stream temperatures have a small range...
```{r, echo = FALSE}
pstage_raw %>%
filter(position != "atmospheric") %>%
  dplyr::summarise(mintemp = min(temperature_C, na.rm = TRUE), maxtemp = max(temperature_C, na.rm = TRUE))
```

where the density will not differ much from one data point to another.

This will generate a dataframe with an added column for 'depth' based on an equation using the difference between the atmospheric pressure and the well pressure on for the same date and time. 
```{r}
pstage_depth <- inner_join(filter(pstage_raw, position =="atmospheric"), 
            filter(pstage_raw,position != "atmospheric"), by= c("datetime")) %>%
  mutate(depth_m = (pressure_kPa.y-pressure_kPa.x)/(0.999*9.98)) %>%
  select(ID.y, datetime, pressure_kPa.x, pressure_kPa.y, depth_m, position.y, instrument_no.y, temperature_C.y)
  
```


```{r, echo = FALSE}
#quick plot of pressure
depth <- ggplot(pstage_depth, aes(datetime, depth_m, color=position.y))+
  geom_line()

ggplotly(depth)
```



# Explore missing timesteps
The check Timesteps function will generate a dataframe of missing timesteps by
showing every row of the input df where the difference between datapoint times does not equal the interval between the first two datapoints.

```{r}

checkTimesteps(pstage_raw)
```

# Look for large data fluctuations

1) Plot temperature for quick checks
2) Plot raw data with flag if raw level changes by more than x%. 

```{r}

threshold <-5
pstage_list <- split(pstage_raw, pstage_raw$position)
temp_list <- lapply(pstage_list, function(x) {
  cbind(x, flag = ifelse(c(0,abs(diff(x$temperature_C)))/x$temperature_C > threshold, 48, 1)) })
tempall <- do.call(rbind, temp_list) 
tempall <-  tempall[c('temperature_C', 'ID', 'datetime', 'position')]

tempall <-tempall %>%
  tibble::rowid_to_column() %>%
  spread(key = position, value = temperature_C)

# The number in temp_list[[]] is indicative of position
tsTemp <- xts(tempall, order.by = as.POSIXct(tempall$datetime))

dygraph(tsTemp) %>% 
            #adds time series launcher
            dyRangeSelector() %>% 
            #adds highlight/fade (controled by alpha) of series and formats circle.
            dyHighlight(highlightCircleSize = 4, 
                        highlightSeriesBackgroundAlpha = 0.2,
                        hideOnMouseOut = TRUE)%>% 
            dyAxis('y',label='Degree C',valueRange = c(-20,20 ))%>%
            dyAxis('y2',label='ID',independentTicks=T)%>%
            dySeries('ID',axis='y2')%>%
            #Assigns legend to follow cursor, also can choose 'always' to always see it
            dyLegend(show = "always")
```


###compare cleaned water level to manual measurements
```{r}
#plot difference between measured water depth and manual depth measurement
#stageAdj.man<- left_join(manMeas_fil,stage_adj)%>%
#      mutate(diff = man_wtr_dep_static-wtr_depth)

#ggplot(stageAdj.man, aes(datetime, diff))+
#  geom_point(size=3)+
# theme_minimal()
```


```{r}
#plot water level time series with manual measurements as points
#stage_check_plot<- stage_adj%>%
#  left_join(manMeas_fil)%>%
#  ggplot(aes(datetime,wtr_depth))+
#    geom_line()+
#    geom_point(aes(datetime, man_wtr_dep_static),size=3,col='red')

#ggplotly(stage_check_plot)
```

###save
```{r}
#stage_final <- stage_adj%>%
 #     dplyr::select(location, site, datetime, wtr_depth,level_flag)
#loc_site<- paste(location,site, sep='_')

#interfiles <- './data/3_cleaned_stage_caprod'
#file_path <- paste(interfiles,location,site, sep='/')
#saveRDS(stage_final, file=paste0('data/cln/wtr_lvl_',loc_site,'.csv'))
#write_csv(stage_final, file=paste0(file_path, '_clean.csv'))

```



