---
title: "mid-season planning"
author: "Lauren Kremer"
date: '2022-06-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pkgTest <- function(x)
{
  if (x %in% rownames(installed.packages()) == FALSE) {
    install.packages(x, dependencies= TRUE)
  }
  library(x, character.only = TRUE)
}

# Make a vector of the packages you need
neededPackages <- c('ggplot2', 'tidyverse', 'dplyr', 'lubridate', 'plotly', 'ggthemes', 'reshape') #tools for plot titles 

# For every package in the vector, apply your pkgTest function
for (package in neededPackages){pkgTest(package)}
```

#### Review sample frequency 
1. Separating SSFP, outlet monitoring and synoptic monitoring samples by site.
```{r import, include=FALSE}
file_path <- "/Users/laurenkremer/Dropbox/Fraser Experimental Forest/Sample_inventory_chemistry_logs/NSFSampleLog_forR.csv"

dat <- read.table(file_path, skip = 0, header = TRUE, sep = ",", row.names = NULL, as.is = TRUE)
```

```{r format, include=FALSE}
dat <- dat %>%
  mutate(watershed = as.factor(watershed)) %>%
  mutate(site = as.factor(location))

dat <- dat %>%
  mutate(datetime = lubridate::mdy(date) + hm(time)) %>%
  mutate(date = lubridate::mdy(date)) %>%
  mutate(year = lubridate::year(date)) %>%
  filter(type != 'monitoring')
```

```{r plot1, echo = FALSE, message=FALSE, fig.show ='hide'}

ggplot(dat, aes(date, fill = sample)) +
# Create ggplot2 histogram with default colors
  geom_histogram() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %y") +
  facet_wrap(~type, nrow = 3) +
  ylab('Sample count') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(
  # Hide panel borders and remove grid lines
  #panel.border = element_blank(),
  panel.background = element_rect(fill = "white"),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  # Change axis line
  axis.line = element_line(colour = "black")
  ) +
  scale_fill_manual(values=c("#66FFFF", "#CCFF66", "#000066", "#FFCC66")) +
  guides(fill=guide_legend(title="Sample source"))
    
```

```{r plot2, echo = FALSE, message=FALSE}

summdat <- dat %>%
  filter(watershed != 'ssfp')

# New facet label names for watershed variable
watershed.labs <- c("Deadhorse", "E.St.Louis", "Fool Creek", "Lexen")
names(watershed.labs) <- c("dh", "E. St. Louis", "fc", 'lexen')

ggplot(summdat, aes(date, fill = sample)) +
# Create ggplot2 histogram with default colors
  geom_histogram(binwidth = 14) +
  scale_x_date(date_breaks = "3 months", date_labels = "%d %b %y") +
  facet_grid(watershed ~ type, labeller = labeller(watershed = watershed.labs)) +
  ylab('Sample count') +
  theme_bw() +
  scale_fill_manual(values=c("#000066", "#FFCC66")) +
  theme(axis.text.x = element_text(angle = 90),
        strip.text.y = element_text(size = 8))
  
```

2. Subset SSFP, outlet monitoring and synoptic monitoring samples, and plot by sample type (e.g., DOC, IC, respiration/BOD, FTICR-MS, fluorescence/EEM)

#### Watersheds
```{r plot3, echo = FALSE, message=FALSE}

summdat <- dat %>%
  select('watershed', 'sample', 'type', 'FTICR.MS', 'Fluorescence', 'Respiration', 'DOC', 'IC', 'date') %>%
  gather(sampletype, value, -c(watershed, sample, type, date)) %>%
  group_by(date, watershed, sample, type, sampletype) %>%
  as.data.frame()

#convert character columns into factor columns
cols <- c('sample', 'type', 'sampletype')
summdat[cols] <- lapply(summdat[cols], as.factor)

plotdat <- summdat %>%
  filter(watershed != 'ssfp')

# New facet label names for watershed variable
watershed.labs <- c("Deadhorse", "E.St.Louis", "Fool Creek", "Lexen")
names(watershed.labs) <- c("dh", "E. St. Louis", "fc", 'lexen')

ggplot(as.data.frame(plotdat), aes(x = date, fill = sampletype)) +
# Create ggplot2 histogram with default colors
  geom_histogram() +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %y") +
  facet_grid(watershed ~ sample, labeller = labeller(watershed = watershed.labs)) +
  ylab('Sample count') +
  theme_bw()  +
  scale_fill_manual(values=c("#330033", "#990099", "#330099", "#6666FF", "#66CCFF")) +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_text(angle = 0),
        strip.text.y = element_text(size = 8))
  
```

#### Subsurface Flowplots
```{r plot4, echo = FALSE, message=FALSE}
plotdat <- summdat %>%
  filter(watershed == 'ssfp')

ggplot(as.data.frame(plotdat), aes(x = date, fill = sampletype)) +
# Create ggplot2 histogram with default colors
  geom_histogram(binwidth = 14) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %y") +
  facet_grid(~ sample) +
  ylab('Sample count') +
  theme_bw()  +
  scale_fill_manual(values=c("#330033", "#990099", "#330099", "#6666FF", "#66CCFF")) +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_text(angle = 0),
        strip.text.y = element_text(size = 8))

```






## NEXT STEP IS TO ADD STAGE
## IMPORT CLEAN STAGE DATA FOR EACH OUTLET - CONCATONATED BY YEAR
```{r}

opn_clean <- function(interfiles, year, watershed, site) {
   file_path <-  paste(getwd(), '/', interfiles, '/', year, '/', watershed, '/', site, '/', site, '_clean.csv', sep = '')
   dat <- read.table(file_path, skip = 0, header = TRUE, sep = ",", row.names = NULL, as.is = TRUE) %>%
    rowid_to_column(var='ID') %>%
    mutate(datetime = ymd(date) + hm(time))%>%
    arrange(datetime) %>%
    drop_na()
    return(dat)
   }
```

```{r}
interfiles <- 'clean_data/stage_caprod'
# possible locations: 'dh', 'est_louis', 'fool', 'lexen'
year <- 2020
watershed <- 'dh'
site <- paste(watershed, '1', sep = '')

stage_clean <- opn_clean(interfiles, year, watershed, site) 

```


```{r}
#quick plot of stage

ggplot(stage_clean, aes(datetime, wtr_depth))+
  geom_line()

```

# merge clean stage data with sample data
  1. summarize stage data by day
  
```{r}
stage_clean_summ <- stage_clean %>%
  group_by(date) %>%
  summarize(dmean_wtr_depth = mean(wtr_depth)) %>%
  mutate(date = lubridate::date(date))

ggplot(stage_clean_summ, aes(date, dmean_wtr_depth)) +
  geom_line() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylab('Water level (mm)') +
  scale_y_continuous(breaks = round(seq(170, 310, by = 10),1)) +
  xlab('Date')
  
```

## Now that we've got code for one year and site, lets loop through years to generated a concatonated (2020 - 2022)  stage dataset for each outlet

```{r}
opn_allstg <- function(interfiles) {
  file_path <- paste(getwd(), interfiles, sep='/')
  path_list <- paste(file_path, list.files(file_path, recursive = TRUE), sep= '/')
  data <- lapply(path_list, function(x) {
      dat <- read.table(x, skip = 0, header = TRUE, sep = ",", row.names = NULL, as.is = TRUE) %>%
        rowid_to_column(var='ID') %>%
        mutate(datetime = ymd(date) + hm(time))%>%
        arrange(datetime) %>%
        drop_na()
      dat$watershed <- unlist(strsplit(x, "/"))[10]
      dat$site <- unlist(strsplit(x, "/"))[11]
      return(dat)
  })
  combined_data <- do.call(rbind, data)%>%
  arrange(datetime)
  return(combined_data)
}
```


```{r}
allyrs_stage_clean <- opn_allstg(interfiles)
```

```{r}
allyrstage_summ <- allyrs_stage_clean %>%
  select (-c(ID, time, level_flag, datetime)) %>%
  mutate(date = lubridate::date(date)) %>%
  mutate(watershed = as.factor(watershed)) %>%
  group_by(date, watershed, site) %>%
  summarize(dmean_wtr_depth = mean(wtr_depth))%>%
  mutate(year = lubridate::year(date)) %>%
  as.data.frame()
  
  
ggplot(subset(allyrstage_summ, watershed == 'dh'), aes(date, dmean_wtr_depth, group = year)) +
  geom_line() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y") + 
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylab('Water level (mm)') +
  xlab('Date') 
```

```{r}
ggplot(subset(allyrstage_summ, watershed == 'lexen'), aes(date, dmean_wtr_depth, group = year)) +
  geom_line() +
  theme_classic() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylab('Water level (mm)') +
  xlab('Date') 

```


# merge sample counts with daily water level
```{r}

summdat_nossfp <- summdat %>%
  filter(watershed != 'ssfp')

stageclean_w_sampcount <- merge(allyrstage_summ, summdat_nossfp, by = c("date","watershed"), all=T)
```



```{r}
dhplot <- subset(stageclean_w_sampcount, watershed == 'dh')
ybreaks = seq(0, 150,25)
n_obs = sum(!is.na(dhplot$value))

ggplot(data = subset(dhplot, !is.na(sampletype)), mapping = aes(x = date, fill = sampletype)) +
  geom_histogram(binwidth = 14) +
  geom_line(dhplot, mapping = aes(x = date, y = (dmean_wtr_depth)/2, group = 1),inherit.aes = FALSE, color = 'blue') +
  scale_y_continuous("counts", breaks = round(ybreaks), labels = ybreaks, sec.axis = sec_axis(~.*2, breaks = round(seq(50, 310, by = 20),1), name = "Daily mean stage (mm)")) +
  theme_bw() + # the first is y_axis for histogram, sec.axis establishes second axis. The issue here is that the user has to establish a multiple that aligns the second axis with the data correctly. 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_x_date(date_breaks = "2 months", date_labels = "%d %b %Y") 

  
```







